\section{Abstracts and Presentations}
\cvitem{2013}{\uline{\textbf{Willis JR}}, Crowe JE, Meiler J. Broadly neutralizing antibodies to HIV in HIV-na\"{i}ve donor populations. The broadly neutralizing antibody problem. Chemical and Physical Biology Symposium, Vanderbilt University}
\cvitem{2013}{\uline{Finn JA}, Nannemann, DP, \textbf{Willis JR}, Crowe JE, Meiler J. \textit{De novo} modeling of antibody CDRH3 loops with constraints. RosettaCon}
\cvitem{2012}{\uline{\textbf{Willis JR}}, Briney BS, Meiler J, Crowe JE. Potential paradigm shifts in HIV vaccine design using ultra high-throughput sequencing and antibody modeling. Chemical and Physical Biology Symposium}
\cvitem{2012}{\uline{Briney BS}, \textbf{Willis JR}, Crowe JE. Somatic hypermutation-associated insertions and deletions reveal regions of antibody structural plasticity. Keystone symposium on HIV Vaccines}
\cvitem{2012}{\uline{Finn JA}, \textbf{Willis JR}, Briney, BS, Crowe JE, Meiler J. Structural prediction of long complementarity determining region 3 loops. RosettaCon}
\cvitem{2012}{\uline{\textbf{Willis JR}}, Briney BS, Meiler J, Crowe JE. Structure analysis of healthy donor repertoire confers sequences that match long complementarity determining regions of broadly neutralizing antibodies. Keystone Symposium on HIV Vaccines}
\cvitem{2011}{\uline{Briney BS}, \textbf{Willis JR}, Crowe JE. Genetic and functional analysis of the human anti-HIV antibody repertoire. Keystone Symposium on HIV Vaccines}
\cvitem{2011}{\uline{\textbf{Willis JR}}, Crowe, JE, Meiler J. Multi-state design of antibody-antigen interactions confers conformational flexibility. RosettaCon}
\cvitem{2011}{\uline{Briney BS}, \textbf{Willis JR}, Crowe JE. Genetic origin of long HCDR3s in the circulating antibody repertoire. IBC Life Sciences - Antibody Engineering \& Therapeutics}
\cvitem{2011}{\uline{\textbf{Willis JR}}, Crowe, JE, Meiler J. Structural basis for development of broadly neutralizing antibodies to HIV using computational predictions. Chemical and Physical Biology Symposium.}
\cvitem{2011}{\uline{\textbf{Willis JR}}, Briney, BS, Crowe, JE, Meiler J. Antibody design infers optimal sequences for binding breadth and affinity maturation. IBC Life Sciences - Antibody Engineering \& Therapeutics}
\cvitem{2010}{\uline{\textbf{Willis JR}}, Crowe, JE, Meiler J. Constrained design of broadly neutralizing HIV antibody-antigen interactions. RosettaCon}
\cvitem{2009}{\uline{\textbf{Willis JR}}, Meiler, J, Crowe JE. HIV gp160 targeted broadly neutralizing antibodies - modeling and design. RosettaCon}

