\section{Research Publications}
\cvitem{2017}{Kulp DW, Steichen JM, Pauthner M, Hu X, Schiffner T, Liguori A, Cottrell CA, Havenar-Daughton C, Ozorowski G, Georgeson E, Kalyuzhniy O, \textbf{Willis JR}, Kubitz M, Adachi Y, Reiss SM, Shin M, de Val N, Ward AB, Crotty S, Burton DR, Schief WR, Structure-based design of native-like HIV-1 envelope trimers to silence non-neutralizing epitopes and eliminate CD4 binding. \textit{Nat Commun} \textbf{8}: 1655}
\cvitem{2017}{Sarkar U, Hillebrand R, Johnson KM, Cummings AH, Phung NL, Rajapakse A, Zhou H, \textbf{Willis JR}, Barnes CL, Gates KS, Application of Suzuki-Miyaura and Buchwald-Hartwig Cross-coupling Reactions to the Preparation of Substituted 1,2,4-Benzotriazine 1-Oxides Related to the Antitumor Agent Tirapazamine. \textit{J Heterocycl Chem} \textbf{54}: 155-160}
\cvitem{2016}{Hicar MD, Chen X, Sulli C, Barnes T, Goodman J, Sojar H, Briney B, \textbf{Willis J}, Chukwuma VU, Kalams SA, Doranz BJ, Spearman P, Crowe JE Jr, Human Antibodies that Recognize Novel Immunodominant Quaternary Epitopes on the HIV-1 Env Protein. \textit{PLoS One} \textbf{11}: e0158861}
\cvitem{2016}{Boehme KW, Ikizler M, Iskarpatyoti JA, Wetzel JD, \textbf{Willis J}, Crowe JE Jr, LaBranche CC, Montefiori DC, Wilson GJ, Dermody TS, Engineering Recombinant Reoviruses To Display gp41 Membrane-Proximal External-Region Epitopes from HIV-1. \textit{mSphere} \textbf{1}: None}
\cvitem{2016}{Finn JA, Koehler Leman J, \textbf{Willis JR}, Cisneros A 3rd, Crowe JE Jr, Meiler J, Improving Loop Modeling of the Antibody Complementarity-Determining Region 3 Using Knowledge-Based Restraints. \textit{PLoS One} \textbf{11}: e0154811}
\cvitem{2016}{\textbf{Willis JR}, Finn JA, Briney B, Sapparapu G, Singh V, King H, LaBranche CC, Montefiori DC, Meiler J, Crowe JE Jr, Long antibody HCDR3s from HIV-naive donors presented on a PG9 neutralizing antibody background mediate HIV neutralization. \textit{Proc Natl Acad Sci U S A} \textbf{113}: 4446-51}
\cvitem{2015}{\textbf{Willis JR}, Sapparapu G, Murrell S, Julien JP, Singh V, King HG, Xia Y, Pickens JA, LaBranche CC, Slaughter JC, Montefiori DC, Wilson IA, Meiler J, Crowe JE Jr, Redesigned HIV antibodies exhibit enhanced neutralizing potency and breadth. \textit{J Clin Invest} \textbf{125}: 2523-31}
\cvitem{2014}{Briney BS, \textbf{Willis JR}, Finn JA, McKinney BA, Crowe JE Jr, Tissue-specific expressed antibody variable gene repertoires. \textit{PLoS One} \textbf{9}: e100839}
\cvitem{2014}{Lin D, He H, Ji H, \textbf{Willis J}, Willard L, Jiang Y, Medeiros DM, Wark L, Han J, Liu Y, Lu B, Wolfberries potentiate mitophagy and enhance mitochondrial biogenesis leading to prevention of hepatic steatosis in obese mice: the role of AMP-activated protein kinase alpha2 subunit. \textit{Mol Nutr Food Res} \textbf{58}: 1005-15}
\cvitem{2013}{Combs SA, Deluca SL, Deluca SH, Lemmon GH, Nannemann DP, Nguyen ED, \textbf{Willis JR}, Sheehan JH, Meiler J, Small-molecule ligand docking into comparative models with Rosetta. \textit{Nat Protoc} \textbf{8}: 1277-98}
\cvitem{2013}{\textbf{Willis JR}, Briney BS, DeLuca SL, Crowe JE Jr, Meiler J, Human germline antibody gene segments encode polyspecific antibodies. \textit{PLoS Comput Biol} \textbf{9}: e1003045}
\cvitem{2012}{Briney BS, \textbf{Willis JR}, Hicar MD, Thomas JW 2nd, Crowe JE Jr, Frequency and genetic characterization of V(DD)J recombinants in the human peripheral blood antibody repertoire. \textit{Immunology} \textbf{137}: 56-64}
\cvitem{2012}{Briney BS, \textbf{Willis JR}, Crowe JE Jr, Human peripheral blood antibodies with long HCDR3s are established primarily at original recombination using a limited subset of germline genes. \textit{PLoS One} \textbf{7}: e36750}
\cvitem{2011}{Joyner AS, \textbf{Willis JR}, Crowe JE Jr, Aiken C, Maturation-induced cloaking of neutralization epitopes on HIV-1 particles. \textit{PLoS Pathog} \textbf{7}: e1002234}\
\vspace{0.2cm}
\cvitem{In Press }{\textbf{Willis JR} et al A generalized HIV vaccine design strategy for priming of broadly neutralizing antibody responses \textit{Science}}
\cvitem{In Progress}{\textbf{Willis JR}, Briney, BS, Schief WR, Precursor frequency focused immunogen design for V1V2-apex bNAbs}
