%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{casual}                             % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                               % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{Jordan}{Willis, PhD}
\title{}                               % optional, remove / comment the line if not wanted
\address{3932 Jewell St}{San Diego CA 92109}{USA}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
\phone[mobile]{+1~(816)~674~5340}                   % optional, remove / comment the line if not wanted
\email{jwillis0720@gmail.com}                               % optional, remove / comment the line if not wanted
\homepage{www.linkedin.com/in/jwillis0720/}                         % optional, remove / comment the line if not wanted

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%-----       letter       ---------------------------------------------------------
% recipient data
\recipient{Pfizer Recruitement}{Pfizer \\La Jolla, CA}
\date{ 2019}
\opening{Dear Pfizer Hiring Manager}
\closing{Sincerely}
%\enclosure[Attached]{JRW curriculum vit\ae{}}          % use an optional argument to use a string other than "Enclosure", or redefine \enclname
\makelettertitle


Considering my background as a Computational Biologist in the field of Immunology and Protein Engineering, I’m excited to be applying for the
Principal Scientist position at Pfizer. 
For the past 14 years I have developed diverse skillset that remarkably intersects with the qualifications you seek. Given the opportunity, 
I'm eager to apply my talents at Pfizer using structure-based antibody modeling.

\vspace{0.1in}
While working on my doctoral thesis in the field of antibody design, my research project involved one of the first applications of next-generation 
sequencing to characterizing B cell repertoires.
I also joined the Rosetta Commons as a developer and pioneered antibody design algorithms which incorporated next-generation sequencing datasets. My research influenced the nexus of applied molecular modeling for antibodies as it's now a common part of most antibody development pipelines. I was also in a unique dual 
mentor program spending half my time in the wet-lab carrying out the experimentation necessary to validate my computational work. This gave me an advantage 
of learning both the computational and experimental sides of antibody engineering.

\vspace{0.1in}
My post doctoral work in the laboratory of William Schief expanded my skillset by adding display technology and library design. I used Rosetta to inform 
mammalian and yeast 
display and was able to engineer the first vaccine able to selectively induce rare antibodies with long HCDR3 sequences.  

For the past year, I have transitioned to industry as a 
Senior Scientist in Computational Biology. I have developed new algorithms to design novel peptides to shape phage display libraries. I also started shaping molecular modeling with protein dynamics and deep learning algorithms. Recently, I was recruited for a Principal Scientist of protein engineering to develop immunologically silent AAV capsids. Currently, I am doing independent consulting for smaller companies needing bioinformatic or protein engineering solutions. 

\vspace{0.1in}
I’m looking forward to learning more details about the Principal Scientist position at Pfizer. I'm very committed individual and have a tremendous amount
 to offer a company like Pfizer.
Feel free to contact my by email or phone attached at the bottom of this letter. 

\makeletterclosing

\end{document}


%% end of file `template.tex'.
