\chapter*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}
\vspace{7mm}
This work would not of been possible without the following people.
First and foremost I would like to thank my two mentors, James Crowe and Jens Meiler. The general consensus of the biomedical science community is that principal investigators often dislike interdepartmental collaboration. When I talk to other graduate students, I find that they have many unpleasant experiences with just a single investigator. I feel very fortunate to have two PIs in which I got along so well with. From opposite ends of the spectrums of science, they never objected to such a collaboration were only a few years ago may have been unavailing. Both of you are an inspiration to my scientific future. Jens with his incredible and often frustrating brilliance of the task at hand, and Jim with his scientific leadership, I could not have asked for two better bosses to nurture my scientific growth.

I would lake to thank all my colleagues in the Crowe and Meiler Labs. An early thanks goes to Kristian Kaufmann, Ralf Mueller, and Mark Hicar, as their initial guidance through my rotation was a deciding factor in my choice for the future. There is innumerable scientific colleagues who helped me with my work including Jessica Finn who helped with the high throughput sequencing, Mark Hicar who taught me about HIV virology, Sam DeLuca who would answer every question I had about computers, Gordon Lemmon who taught me Python, Natalie Thornburg for teaching me many molecular biology techniques. I would also like to thank the lab technicians who made this throughput of work possible, Rachelle Falk, Vidisha Singh, and Hannah King. I would like to make a very special mention to my very good friend and colleague Bryan Briney, who taught me almost everything I know about immunology and high throughput sequencing. Our names appear together on many publications for good reason.

I want to thank my friends and family. Graduate school is a long arduous process and without them I would not be where I am today. First, my sister, who I cannot live up to. You have a heart of gold. My Mother, my number one fan. Her constant encouragement has helped me survive graduate school. I'm lucky to have her in my life and to have spent a majority of my time in Nashville with her close. She is a great source of inspiration in all that I do. A constant drive and loving force. My Father, my role model. His support for me has been tremendous. His drive and motivation showed me what a little hard work can do. I hope to become half-the man he is today. My friends, helping me keep sanity through graduate school. I would especially like to thank Sean Welch, who allowed me sanctuary away from graduate school. You are also a tremendous inspiration. Lastly I would like to thank my best friend in graduate school, my cat Ocho, the only constant through these last six years. I love you little buddy! Here's to many more years together.
