%This is a comment, it will not be compiled...

\listfiles
\documentclass[12pt]{report}
\usepackage[intoc]{nomencl}

% \textwidth=6in
% \oddsidemargin=0.2in
% \topmargin=-0.5in
% \textheight=9in  % 9in must include page numbers
% \textfloatsep=0.4in \addtocontents{toc}{\vspace{0.4in} \hfill
% Page\endgraf} \addtocontents{lof}{\vspace{0.2in} \hspace{0.13in} \
% Figure\hfill Page\endgraf} \addtocontents{lot}{\vspace{0.2in}
% \hspace{0.13in} \ Table\hfill Page\endgraf}

\usepackage[margin=1in]{geometry}

%\usepackage{enumitem}
\usepackage{hyphenat}
\usepackage{siunitx}
\usepackage{fancyvrb}
\usepackage{amsmath}
\usepackage{rotating}
\usepackage[export]{adjustbox}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{array}
\usepackage{listings}
\usepackage{tabularx}
\usepackage{setspace}
\usepackage{mathptmx}
\usepackage[table, svgnames]{xcolor}
\usepackage{colortbl}
\usepackage{graphicx}
\usepackage{amssymb, amsmath}
\usepackage{subfig}
\usepackage{epsfig}
\usepackage{times}
\usepackage{float}
\usepackage{pbox}
\usepackage{rotating}
\usepackage{makeidx}
\usepackage{url}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage[subfigure, titles]{tocloft}
\usepackage[printonlyused,withpage]{acronym}
\usepackage{datetime}
\usepackage{fancyvrb}
\usepackage{color}
\usepackage[autostyle,english=american]{csquotes}
\usepackage{wrapfig}
\usepackage{fixltx2e}
\usepackage[shortcuts]{extdash}
\usepackage{sidecap}
\usepackage{lipsum}
%\usepackage[demo]{graphicx}
\MakeOuterQuote{"}

%%another algorithm package
\usepackage{algorithm}
\usepackage{algorithmic}


\usepackage{paralist}
\usepackage{sidecap}
\usepackage{listings}



\setcounter{secnumdepth}{7}
\setcounter{tocdepth}{7}
\usepackage{hyperref}
\hypersetup{
    pdftitle={Rational Design of Antibodies: From Mechanisms of Specificity to Novel Vaccine Strategies},
    pdfauthor={Jordan Willis},
    bookmarksnumbered, %Determined if chapter numbers are included in the bookmark list
    pdfstartview={FitH},
    pdfborder={0 0 0},
    plainpages=false
}%
\usepackage[all]{hypcap}
\usepackage{amsmath} % or simply amstext
\newcommand{\angstrom}{\text{\normalfont\AA}}

% Stats table label
\newcommand{\statslabel}[2]{\multirowcell{#1}[-1.6mm][c]{#2}}

% Below heading rule.
\newcommand{\otoprule}{\midrule[\heavyrulewidth]}


%For title page
\newcommand*{\SignatureAndDate}[1]{%
    \setlength{\parskip}{0cm}
    \par\noindent\makebox[4.0in]{Approved~\hrulefill} \hfill\makebox[2in]{Date~\hrulefill}%
    \par\noindent\makebox[4.0in][l]{#1}      \hfill\makebox[3in][l]{}%
   \\[0.15in]%
}%

\newenvironment{bottompar}{\par\vspace*{\fill}}{\clearpage}


\interfootnotelinepenalty=10000 %prevents the splitting of long footnotes across multiple pages. Use with caution.

%%Put useful shortcuts here:
\newcommand{\ki}{K$_{i}$}
\newcommand{\ic}{IC$_{50}$ }
\newcommand{\mcml}{$\mu$g/mL}
\newcommand{\ec}{EC$_{50}$ }
\newcommand{\naive}{na\"{i}ve}
\newcommand{\silico}{\textit{in silico}}
\newcommand{\rosetta}{R\textsc{osetta}}
\newcommand{\rosettadesign}{R\textsc{osetta}D\textsc{esign}}
\newcommand{\scripts}{R\textsc{osetta}S\textsc{cripts}}
\newcommand{\ddg}{$\Delta\Delta$G}
\newcommand{\microliter}{$\mu$L}
\newcommand{\degree}{$^{\circ}$}


%Finally we will begin the thesis
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Prevent the warning: pdfTeX warning (ext4): destination with the same identifier (name{page.1}) has been already used, duplicate ignored
%%  This setting will make a difference to the output because the page number is suppressed for the title page
%nonnumeric page numbering
\begin{titlepage}

\begin{flushright}
\textbf{\underline{CHEMICAL AND PHYSICAL BIOLOGY}}
\end{flushright}
\doublespacing
\begin{center}
\setlength{\parskip}{10pt}
    Rational Design of Antibodies: \\ From Mechanisms of Specificity to Novel Vaccine Strategies \\ [.3in]
    Jordan R. Willis \\ [.3in]
\underline{Dissertation under the direction of Professors James E. Crowe Jr. and Jens Meiler}
\end{center}

\setlength{\parindent}{15pt} Human antibodies are critical for eradication of viral and bacterial infections, while providing the basis for immunological memory. Antibody design using the molecular modeling suite \rosetta~is used to answer questions about the molecular basis for antibody polyspecificty as a function of sequence maturation. Germline antibody sequences were found to be the molecular basis for polyspecificity as they can adopt the multiple conformations needed to bind a seemingly infinite antigen structural space. Mature sequences by contrast, are optimized for specificity against one antigen. \\
\indent Antibody design using \rosetta~was extended to interrogate the antibody structural repertoire of HIV-\naive~donor patients to search for patterns that may mimic PG9, a broadly neutralizing antibody against HIV. Broadly neutralizing antibodies against HIV were thought to be the result of years of chronic infection and selective pressure. However, several antibodies were found with modest neutralization potency against HIV indicating that neutralizing antibodies may be prevalent in the HIV-\naive~donor repertoire. This finding has several implications for new vaccine strategies. \\
\indent Finally, \rosettadesign~was used for the redesign of contemporary antibodies against HIV to investigate whether the immune system has fully optimized broadly neutralizing antibodies for maximum potency and breadth. Antibody design was able to find mutations that increase potency and breadth against HIV.

%%%%%%Uncomment  for Approved Names%%%%%%
\begin{center}
\begin{singlespace}
\begin{bottompar}
\SignatureAndDate{James E. Crowe, Jr., M.D. (Advisor)}
\end{bottompar}
\end{singlespace}
\end{center}
\end{titlepage}
\end{document}
