\chapter*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}
\vspace{7mm}

%funding
Much of the work presented here was funded by a pre-doctoral fellowship in informatics from the PhRMA foundation.
%jens
I would like to thank my advisor, Dr. Jens Meiler, for his guidance, and mentoring over the course of my PhD.
Without the insight and support, i would not have been able to 
%committee
I would also like to thank the members of my thesis committee, Dr. Terry Lybrand, Dr. Brian Bachmann, Dr. Heidi Hamm, and Dr. Stephen Fesik for their advice and guidance.
Rosetta is a collaborative project, and this work would not have been possible without the help of a number of people in the Meiler lab and the RosettaCommons as a whole.
Gordon Lemmon and Kristian Kaufmann were instrumental in helping me get started with my work, and with their advice, friendship and mentoring throughout my PhD.
In addition to coping with sitting next to me for 6 years, I would like to thank Steven Combs for being a great friend and colleague, and for helping me deal with science, graduate school, and life in general.

RosettaHTS could not exist in its present form without the ability to rapidly store information in a database.
Developing the infrastructure necessary to accomplish this was a tremendous undertaking, and would have been impossible to complete without the collaboration of Matt O'Meara and Tim Jacobs at UNC North Carolina.
Will Lowe, Mariusz Butkiewicz, and Jeff Mendenhall kindly took the time to teach me the fundamentals of Artificial Neural Networking, answer my endless questions, and brainstorm ideas about incorporating ANN methods with Rosetta screening.
Their help was instrumental to the work described in chapter \ref{chap:rosetta_hts}.
Darwin Fu, Brittany Allison, Thomas Austin, Jordan Willis, and Amanda Duran have been vital to the development of the work described in this thesis both through their direct contributions, and through their feedback as they used the software tools described here.

Graduate school is a long and arduous process, and I would not have been able to complete it without friends.
In addition to those mentioned above, I'd like to acknowledge Steven Combs, Thuy Nguyen, Liz Nguyen, Sten Heinze, Kate Mittendorf, Mert Karakas, Julia Koehler, Andrew Morin, and Ralf Mueller at Vanderbilt University.%TODO others?
I would also like to acknowledge  Vanderbilt, Andrew Leaver-Fay at UNC Chapel Hill, Doug Renfrew at New York University, Brian Weitzner, Jason Labonte, and Jared Adolf-Bryfogle at John Hopkins. %TODO others?
I will be forever grateful for their friendship over the past 6 years.
Stephanie DeLuca, %TODO: think about this one
%steph
Alice and Ed, my parents, and Marie, my sister, are the best family one could ask for.  I would not be where I am right now if not for their endless support and encouragement.

My path to this point in my education has been a long one, and I credit several of my early teachers for helping set me along this road.
I credit Janine, Keith and Ken Baker for teaching me the joy of computer programming, and Dr. David Form and Dr. Mary Jane Kurtz for showing me how %TODO: messy

%family
%cat

Finally, I would like to dedicate this thesis in memory of my grandather, Eldon Boling.
Eldon was a doctor, scientist, and inventor, and his kindness and gift for asking the next question has been an inspiration to me. 
